Tutorial: SQL-on-Hadoop Systems

### 2015-04-02 paper.tex
file format edits

{\em Avro} uses JSON for defining data types and protocols, and compacts data in a binary format. 
{\em SequenceFiles} are flat files of key/value pairs.
While popular there are some column-oriented, more accurately PAX-like \cite{AilamakiDHS01}, file formats: {\em RC}, {\em ORC} and {\em DWRF} \cite{dwrf}, as well as {\em Parquet}.
We present them and perform a comparison between them in terms of usability, data size (compression) and speed of processing

>>>>

{\em Avro} uses JSON for defining data types and protocols, and compacts data in a binary format. 
{\em SequenceFiles} are flat files of key/value pairs. While these formats are widely used for many Hadoop
tasks, column-oriented, more accurately PAX-like \cite{AilamakiDHS01}, file formats are more popularly used with SQL-on-Hadoop systems. These formats include {\em RC}, {\em ORC} and {\em DWRF} \cite{dwrf}, as well as {\em Parquet}. In this tutorial,
we will present these file formats and compare them in terms of usability, data size (compression) and speed of processing.
